Applying Spatio-temporal Scan Statistics and Spatial Autocorrelation Statistics to identify Covid-19 clusters in the world.

### 2021-01-12 Notebooks/paper_covid.rmd
Update paper_covid.rmd

>>>>

  The Poisson Scan Statistic calculated for the number of cumulative cases identified the duration of emerging *clusters* in the number of infections throughout the year, in a comparison of a timeline of events that occurred in the pandemic $\!\!^3$ and the observed *clusters*, since March 25th the US was identified as an emerging *cluster* by the Scan Statistic and one day later the US turned out to be the country with most cases of Covid-19 in the World.
